\vspace{-2cm} \LARGE Divergence-Free Smoothed Particle Hydrodynamics \\ \large Advanced Simulation and Visualization of Fluids in Computer Graphics

### 2016-12-14 report/paper.tex
Restructured method section

@@

@@

The divergence-free solver ensures the fluid to be free of density change over time by enforcing $\frac{D\rho}{Dt} = 0$, which is equivalent to the Navier-Stokes divergence free condition given in equation %\ref{eq:navier}.

The solver will ensure that the divergence error is of an acceptable level defined by the user. The divergence error is suppressed by a combined symmetric pressure force $\vect{F_{j\leftarrow i}^p} $ over all particle $i$'s neighbours $j$, that is applied to the predicted velocity of particle $i$. The pressure force is determined by

@@

% Write about non pressure forces, velocity osv..?
\subsection{Adapted time step}

>>>>

\subsection{Adapted time step}

@@

% Write about non pressure forces, velocity osv..?

@@

The divergence-free solver ensures the fluid to be free of density change over time by enforcing $\frac{D\rho}{Dt} = 0$, which is equivalent to the Navier-Stokes divergence free condition given in equation \ref{eq:nsDensity}.

The solver will ensure that the divergence error is smaller than an acceptable level defined by the user. The divergence error is suppressed by a combined symmetric pressure force $\vect{F_{j\leftarrow i}^p} $ over all particle $i$'s neighbours $j$, that is applied to the predicted velocity of particle $i$. The pressure force is determined by

@@
